---
title: "Group Assignment"
author: "Jiatao Li"
date: "2020/01/10"
output: html_document
---

```{r}
# Load Data
library(readr)
predictors <- read_csv("predictors.csv")
```

```{r}
# Transfer data into time series
library(tseries)
transport_ts = ts(predictors[,3:8],start = c(2005,1),frequency = 12)
```

```{r}
library(dplyr)
library(fpp2)
library(TSA)
# Summary statistics
transport_ts[,"Population"] %>%
  stl(t.window=13, s.window="periodic", robust=TRUE) %>%
  autoplot() + ggtitle("Population")

transport_ts[,"Air"] %>%
  stl(t.window=13, s.window="periodic", robust=TRUE) %>%
  autoplot() + ggtitle("Air")

transport_ts[,"GDP"] %>%
  stl(t.window=13, s.window="periodic", robust=TRUE) %>%
  autoplot() + ggtitle("GDP")
transport_ts[,"ServiceIndustry"] %>%
  stl(t.window=13, s.window="periodic", robust=TRUE) %>%
  autoplot() + ggtitle("ServiceIndustry")
transport_ts[,"MigrantWorker"] %>%
  stl(t.window=13, s.window="periodic", robust=TRUE) %>%
  autoplot() + ggtitle("MigrantWorker")
transport_ts[,"Tourist"] %>%
  stl(t.window=13, s.window="periodic", robust=TRUE) %>%
  autoplot() + ggtitle("Tourist")
```

# Population: ARIMA(0,2,1)
## stationarization
```{r}
library(fpp2)
library(TSA)
autoplot(transport_ts[,"Population"]) + ylab('Population')
#original data has strong trend, need differencing
nsdiffs(transport_ts[,"Population"]) #D=0
ndiffs(transport_ts[,"Population"]) #d=2
ggtsdisplay(diff(transport_ts[,"Population"]))
adf.test(diff(transport_ts[,"Population"])) #after diff once, ts is still not stationary, need diff
ggtsdisplay(diff(diff(transport_ts[,"Population"]))) # AR(3) or MA(1)
adf.test(diff(diff(transport_ts[,"Population"]))) #after diff twice, ts is stationary
```
## choose model
```{r}
fit1 <- auto.arima(transport_ts[,"Population"], d=2, stepwise = FALSE) #ARIMA(0,2,0)(2,0,2)[12]
fit1 #all coefficients are not significant
```
```{r}
fit1.ar3 <- Arima(transport_ts[,"Population"], order = c(3,2,0))
fit1.ar3 #all coefficients are significant
checkresiduals(fit1.ar3) #residuals is not white noise
fit1.ma1 <- Arima(transport_ts[,"Population"], order = c(0,2,1))
fit1.ma1 #all coefficients are significant
checkresiduals(fit1.ma1) #residuals is white noise
#final model: ARIMA(0,2,1)
Population_stationary <- diff(diff(transport_ts[,"Population"]))
Population <- transport_ts[,"Population"]
```
## predict
```{r}
fc1 <- forecast(fit1.ma1,h=13)
fc1
autoplot(fc1) + ylab('Population')
autoplot(fc1, xlim = c(2017,2021), ylim = c(138000,142000))
```


# Migrant Worker: ARIMA(0,2,0)(2,0,0)[12]
## stationarization
```{r}
autoplot(transport_ts[,"MigrantWorker"])
nsdiffs(transport_ts[,"MigrantWorker"])#D=0
ndiffs(transport_ts[,"MigrantWorker"])#d=2
ggtsdisplay(diff(transport_ts[,"MigrantWorker"]))
adf.test(diff(transport_ts[,"MigrantWorker"])) #after diff once, ts still not stationary
ggtsdisplay(diff(diff(transport_ts[,"MigrantWorker"]))) #seasonal AR(2) or seasonal MA(2)
adf.test(diff(diff(transport_ts[,"MigrantWorker"]))) #after diff twice, ts is stationary
```
## choose model
```{r}
fit2 <- auto.arima(transport_ts[,"MigrantWorker"], d = 2, stepwise = FALSE) #ARIMA(0,2,0)(2,0,1)[12]
fit2 #all variables are significant
checkresiduals(fit2) #residuals is whitenoise
autoplot(fit2)
```
```{r}
#seasonal AR
fit2.sar2 <- Arima(transport_ts[,"MigrantWorker"], order = c(0,2,0), seasonal = c(2,0,0))
fit2.sar2 #sar1 is not significant
fit2.sar2.1 <- Arima(transport_ts[,"MigrantWorker"], order = c(0,2,0), seasonal = c(2,0,0), fixed = c(0,NA)) #ARIMA(0,2,0)(2,0,0)[12], sar1 = 0
fit2.sar2.1 #all coefficients are significant, aicc=-1338.62
checkresiduals(fit2.sar2.1) #residuals is whitenoise
autoplot(fit2.sar2.1)
#seasonal MA
fit2.sma2 <- Arima(transport_ts[,"MigrantWorker"], order = c(0,2,0), seasonal = c(0,0,2))
fit2.sma2 #sar2 is not significant
fit2.sma2.1 <- Arima(transport_ts[,"MigrantWorker"], order = c(0,2,0), seasonal = c(0,0,2), fixed = c(0,NA))
fit2.sma2.1 #all coefficients are significant, aicc=-1380.24
checkresiduals(fit2.sma2.1) #residuals is whitenoise
autoplot(fit2.sma2.1) #MA is not invertible, do not take into consideration
```
```{r}
#seasonal ARMA
fit2.sarma <- Arima(transport_ts[,"MigrantWorker"], order = c(0,2,0), seasonal = c(1,0,1)) #ARIMA(0,2,0)(1,0,1)[12]
fit2.sarma #all coefficients are significant, aicc=-1325.87
checkresiduals(fit2.sarma) #residuals past the Ljung-Box test, but ACF lag 24 is significant 
```
```{r}
#cross validation
f2.sar2 <- function(x,h){
  forecast(Arima(x,order = c(0,2,0), seasonal = c(2,0,0)), fixed = c(0,NA), h = h)
}
# f2.sma2 <- function(x,h){
#   forecast(Arima(x,order = c(0,2,0), seasonal = c(0,0,2)),fixed = c(0,NA), h = h)
# }
f2.sarma <- function(x,h){
  forecast(Arima(x,order = c(0,2,0), seasonal = c(1,0,1)),h = h)
}
e1 <- tsCV(transport_ts[,"MigrantWorker"], f2.sar2, h=1)
# e2 <- tsCV(transport_ts[,"MigrantWorker"], f2.sma2, h=1)
e3 <- tsCV(transport_ts[,"MigrantWorker"], f2.sarma, h=1)
#tsCV MSE
mean(e1^2, na.rm = TRUE) #smallest, ARIMA(0,2,0)(2,0,0)[12]
# mean(e2^2, na.rm = TRUE) #smallest, ARIMA(0,2,0)(0,0,2)[12]
mean(e3^2, na.rm = TRUE)
#final model: ARIMA(0,2,0)(2,0,0)[12], ar1=0
MigrantWorker_stationary <- diff(diff(transport_ts[,"MigrantWorker"]))
MigrantWorker <- transport_ts[,"MigrantWorker"]
```
## forecast
```{r}
#from both aicc and tsCV MSE, ARIMA(0,2,0)(2,0,0)[12] is the best model
fc2 <- forecast(fit2.sar2.1, h = 13)
fc2
autoplot(transport_ts[,"MigrantWorker"])+ylab('MigrantWorker')
autoplot(fc2) + ylab('MigrantWorker')
autoplot(fc2, xlim = c(2015,2021), ylim = c(11,14.5))
```


# Tourist
## stationarization
```{r}
autoplot(transport_ts[,"Tourist"])
nsdiffs(transport_ts[,"Tourist"])
ndiffs(transport_ts[,"Tourist"])
ggtsdisplay(diff(transport_ts[,"Tourist"]))
adf.test(diff(transport_ts[,"Tourist"])) #after diff once, ts is still not stationary
ggtsdisplay(diff(diff(transport_ts[,"Tourist"])))
adf.test(diff(diff(transport_ts[,"Tourist"]))) #after diff twice, ts is stationary
```
## choose model
```{r}
fit3 <- auto.arima(transport_ts[,"Tourist"],d = 2, stepwise = FALSE) #ARIMA(0,2,0)(0,0,2)[12]
fit3 #sma2 is not significant
fit3.sma1 <- Arima(transport_ts[,"Tourist"], order = c(0,2,0), seasonal = c(0,0,1))
fit3.sma1 #all coefficients are significant
checkresiduals(fit3.sma1) #residuals is whitenoise
#final model: ARIMA(0,2,0)(0,0,1)[12]
Tourist_stationary <- diff(diff(transport_ts[,"Tourist"]))
Tourist <- transport_ts[,"Tourist"]
```
## forecast
```{r}
fc3 <- forecast(fit3.sma1, h=13)
fc3
autoplot(fc3)
autoplot(fc3, xlim = c(2015,2021), ylim = c(3e+05,7e+05))
```

# GDP
## Transform
```{r}
#Autoplot and transformation
library(fpp2)
GDP = transport_ts[,2]
lambda_GDP <-BoxCox.lambda(GDP)
autoplot(BoxCox(GDP, lambda_GDP)) + ylab('GDP(BoxCox)')
GDP_transformed = BoxCox(GDP, lambda_GDP)
```

## p d q and seasonality

```{r}
library(dplyr)
# Confirm differencing and seasonal differencing
GDP_transformed %>% nsdiffs()
GDP_transformed %>% diff(12) %>% ndiffs()
# Pass the test
GDP_transformed %>% diff(12) %>%diff(lag=1) %>% adf.test()
# Plot Acf,Pacf,Eacf.
library(TSA)
ggtsdisplay(GDP_transformed %>% diff(12) %>% diff(lag=1))
eacf(GDP_transformed %>% diff(12) %>% diff(lag=1))
ggAcf(GDP_transformed %>% diff(12) %>% diff(lag=1))
ggPacf(GDP_transformed %>% diff(12) %>% diff(lag=1))
GDP_stationary <- GDP_transformed %>% diff(12) %>% diff(lag=1)
```

## Model
```{r}
# Choosing 001012 based on Acf Pacf. Adding 1 on pqPQ, we got many candidate model and finally select the one with smallest AICc(013013)
Arima(GDP_transformed, order=c(0,1,1), seasonal=c(0,1,2))
Arima(GDP_transformed, order=c(0,1,3), seasonal=c(0,1,3))

fit_GDP <- Arima(GDP_transformed, order=c(0,1,3), seasonal=c(0,1,3))
fit_GDP %>% residuals() %>% ggtsdisplay()
fit_GDP %>% checkresiduals()
auto.arima(GDP_transformed)

fit_GDP %>% forecast(h=13) %>% autoplot() + ylab('GDP(BoxCox)')
fc_GDP <- fit_GDP %>% forecast(h=13)
```

# Service Industry
## Transform
```{r}
library(fpp2)
SI = transport_ts[,3]
lambda_SI <-BoxCox.lambda(SI)
autoplot(BoxCox(SI, lambda_SI)) + ylab('SI(BoxCox)')
SI_transformed = BoxCox(SI, lambda_SI)
```

## p d q and seasonality

```{r}
library(dplyr)
SI_transformed %>% diff(12) %>% ndiffs()

SI_transformed %>% diff(12) %>% diff(lag=1) %>% adf.test()

library(TSA)
ggtsdisplay(SI_transformed %>% diff(12) %>% diff(lag=1))
eacf(SI_transformed %>% diff(12) %>% diff(lag=1))
ggAcf(SI_transformed %>% diff(12) %>% diff(lag=1))
ggPacf(SI_transformed %>% diff(12) %>% diff(lag=1))
SI_stationary <- SI_transformed %>% diff(12) %>% diff(lag=1)
```

## Model
```{r}
Arima(SI_transformed, order=c(0,1,1), seasonal=c(2,1,1))
Arima(SI_transformed, order=c(0,1,0), seasonal=c(2,1,0))
Arima(SI_transformed, order=c(0,1,0), seasonal=c(2,1,1))
Arima(SI_transformed, order=c(0,1,0), seasonal=c(2,1,2))

fit_SI <- Arima(SI_transformed, order=c(0,1,0), seasonal=c(2,1,0))
fit_SI %>% residuals() %>% ggtsdisplay()
fit_SI %>% checkresiduals()
auto.arima(SI_transformed)

fit_SI %>% forecast(h=13) %>% autoplot() + ylab('SI(BoxCox)')
```


# Air
## Transform
```{r}
library(fpp2)
Air = transport_ts[,1]
lambda_Air <-BoxCox.lambda(Air)
autoplot(BoxCox(Air, lambda_Air)) + ylab('Air(BoxCox)')
Air_transformed = BoxCox(Air, lambda_Air)
```

## p d q and seasonality

```{r}
library(dplyr)
Air_transformed %>% nsdiffs()
Air_transformed %>% diff(12) %>% ndiffs()

Air_transformed %>% diff(12) %>% diff(lag=1) %>% adf.test()

library(TSA)
ggtsdisplay(Air_transformed %>% diff(12) %>% diff(lag=1))
eacf(Air_transformed %>% diff(12) %>% diff(lag=1))
ggAcf(Air_transformed %>% diff(12) %>% diff(lag=1))
ggPacf(Air_transformed %>% diff(12) %>% diff(lag=1))
Air_stationary <- Air_transformed %>% diff(12) %>% diff(lag=1)
```

## Model
```{r}
Arima(Air_transformed, order=c(2,1,0), seasonal=c(2,1,1))
Arima(Air_transformed, order=c(0,1,0), seasonal=c(2,1,1))
Arima(Air_transformed, order=c(0,1,0), seasonal=c(2,1,2))
Arima(Air_transformed, order=c(1,1,0), seasonal=c(2,1,0))
Arima(Air_transformed, order=c(2,1,0), seasonal=c(2,1,0))
Arima(Air_transformed, order=c(1,1,1), seasonal=c(2,1,0))
Arima(Air_transformed, order=c(2,1,1), seasonal=c(2,1,0))
fit_Air <- Arima(Air_transformed, order=c(1,1,1), seasonal=c(2,1,0))
fit_Air %>% residuals() %>% ggtsdisplay()
fit_Air %>% checkresiduals()
auto.arima(Air_transformed)

fit_Air %>% forecast(h=13) %>% autoplot() + ylab('Air(BoxCox)')
fc_Air <- fit_Air %>% forecast(h=13)
```


#Forecast of GDP and ServiceIndustry
```{r}
GDP_forecast12 <- fit_GDP %>% forecast(h=13)
SI_forcast13 <- fit_SI %>% forecast(h=13)
Air_forecast13 <- fit_Air %>% forecast(h=13)
```


```{r}
Population_stationary <- diff(diff(transport_ts[,"Population"]))
Population <- transport_ts[,"Population"]
MigrantWorker_stationary <- diff(diff(transport_ts[,"MigrantWorker"]))
MigrantWorker <- transport_ts[,"MigrantWorker"]
Tourist_stationary <- diff(diff(transport_ts[,"Tourist"]))
Tourist <- transport_ts[,"Tourist"]
```

# Y prediction: Railway ARIMA
```{r}
Railway <- read_csv('RailwayPassengerTrafficVolume(1).csv')[,2]
Y <- ts(Railway, start = c(2005,1), frequency = 12)
```

## stationary
```{r}
autoplot(Y)
BoxCox.lambda(Y)
Y %>% log() %>% autoplot()
Y %>% log() %>% nsdiffs() #1
Y %>% log() %>% diff(12) %>% autoplot() 
Y %>% log() %>% diff(12) %>% adf.test() #still not stationary
Y %>% log() %>% diff(12) %>% ndiffs() #0
Y %>% log() %>% ndiffs() #1
Y %>% log() %>% diff() %>% autoplot()
Y %>% log() %>% diff() %>% adf.test() #stationary
Y %>% log() %>% diff() %>% ggtsdisplay(lag.max = 96) #ACF seasonal lags decay slowly, indicating trend
Y %>% log() %>% diff() %>% nsdiffs() #1
Y %>% log() %>% diff() %>% diff(12) %>% autoplot()
Y %>% log() %>% diff() %>% diff(12) %>% adf.test()
Y %>% log() %>% diff() %>% diff(12) %>% ggtsdisplay(lag.max = 96) #stationary, seasonal MA(2)
```

## choose model:ARIMA(2,1,1)(0,1,2)[12],aicc=-489.36
```{r}
fitY <- auto.arima(log(Y), d = 1, stepwise = FALSE) #ARIMA(2,1,1)(0,1,2)[12]
fitY #all variables are significant
checkresiduals(fitY) #residuals is whitenoise
autoplot(fitY) #
```
```{r}
#D = 1, d = 1, choose P,Q
Arima(log(Y),order = c(0,1,0),seasonal = c(0,1,2)) #all coefficients are significant
Arima(log(Y),order = c(0,1,0),seasonal = c(0,1,2)) %>% checkresiduals() #residuals is not whitenoise
Arima(log(Y),order = c(0,1,0),seasonal = c(0,1,2)) %>% residuals() %>% ggtsdisplay() #MA(3) or ARMA
Arima(log(Y),order = c(0,1,0),seasonal = c(0,1,2)) %>% residuals() %>% eacf() #ARMA(2,1) or MA(3)
```

```{r}
Arima(log(Y),order = c(2,1,1),seasonal = c(0,1,2)) #all coefficients are significant, aicc=-489.36
Arima(log(Y),order = c(2,1,1),seasonal = c(0,1,2)) %>% checkresiduals() #residuals is whitenoise
Arima(log(Y),order = c(0,1,3),seasonal = c(0,1,2)) #ma2 is not significant
Arima(log(Y),order = c(0,1,3),seasonal = c(0,1,2), fixed = c(NA,0,NA,NA,NA)) #all coefficients are significant, aicc = -483.73
Arima(log(Y),order = c(0,1,3),seasonal = c(0,1,2), fixed = c(NA,0,NA,NA,NA)) %>% checkresiduals() #residuals is not whitenoise
```
```{r}
#check redundancy, cannot be redundant
Arima(log(Y),order = c(2,1,1),seasonal = c(0,1,1)) #all coefficients are significant
Arima(log(Y),order = c(2,1,1),seasonal = c(0,1,1)) %>% checkresiduals() #residuals is not whitenoise
Arima(log(Y),order = c(2,1,0),seasonal = c(0,1,2)) #all coefficients are significant
Arima(log(Y),order = c(2,1,0),seasonal = c(0,1,2)) %>% checkresiduals() #residuals is not whitenoise
Arima(log(Y),order = c(1,1,1),seasonal = c(0,1,2)) #ar1 is not significant
Arima(log(Y),order = c(1,1,1),seasonal = c(0,1,2),fixed = c(0,NA,NA,NA)) #all coefficients are significant
Arima(log(Y),order = c(1,1,1),seasonal = c(0,1,2),fixed = c(0,NA,NA,NA)) %>% checkresiduals() #residuals is not whitenoise
```
## forecast
```{r}
fcY <- forecast(fitY, h=13)
fcY
autoplot(fcY)
farimaY <- function(x,h){
  forecast(Arima(x,order = c(2,1,1),seasonal = c(0,1,2)),h=h)
}
e_arimaY <- tsCV(log(Y),farimaY,h=1)
mean(e_arimaY^2,na.rm = TRUE)
```
```{r}
autoplot(ts(exp(append(log(Y),fcY$mean)),start=c(2005,1),frequency = 12)) + ylab("Railway Passenger")
```

# Y prediction: regression with ARIMA residuals
```{r,fig.height=7,fig.width=8}
Y_stationary <- Y %>% log() %>% diff() %>% diff() %>% diff(12)
X <- cbind(GDP_stationary, SI_stationary, Air_stationary, Population_stationary, MigrantWorker_stationary, Tourist_stationary)
X_transformed <- cbind(GDP_transformed, SI_transformed, Air_transformed,Population, MigrantWorker, Tourist)
X_stationary <- X_transformed %>% log() %>% diff() %>% diff() %>% diff(12)
autoplot(X_transformed, facets = TRUE) +
  xlab("Year") + ylab("")
autoplot(X_transformed %>% diff() %>% diff(12), facets = TRUE) +
  xlab("Year") + ylab("")  #not stationary
adf.test(X_transformed[,1] %>% diff() %>% diff() %>% diff(12))
adf.test(X_transformed[,2] %>% diff() %>% diff() %>% diff(12))
adf.test(X_transformed[,3] %>% diff() %>% diff() %>% diff(12))
adf.test(X_transformed[,4] %>% diff() %>% diff() %>% diff(12))
adf.test(X_transformed[,5] %>% diff() %>% diff() %>% diff(12))
adf.test(X_transformed[,6] %>% diff() %>% diff() %>% diff(12))

autoplot(X_transformed %>% diff() %>% diff() %>% diff(12),facets = TRUE) #stationary
autoplot(X_transformed %>% diff() %>% diff(),facets = TRUE) #not stationary
autoplot(X_transformed %>% diff(12) %>% diff(12),facets = TRUE) #not stationary

autoplot(X_transformed %>% diff() %>% diff() %>% diff(),facets = TRUE) #stationary
adf.test(X_transformed[,1] %>% diff() %>% diff() %>% diff())
adf.test(X_transformed[,2] %>% diff() %>% diff() %>% diff())
adf.test(X_transformed[,3] %>% diff() %>% diff() %>% diff())
adf.test(X_transformed[,4] %>% diff() %>% diff() %>% diff())
adf.test(X_transformed[,5] %>% diff() %>% diff() %>% diff())
adf.test(X_transformed[,6] %>% diff() %>% diff() %>% diff())
```
```{r,fig.height=7,fig.width=8}
autoplot(transport_ts[,c("GDP","ServiceIndustry","Air","Population","MigrantWorker","Tourist")], facets = TRUE) +
  xlab("Year") + ylab("Original")
```


```{r,fig.height=7,fig.width=8}
X_transformed.1 <- X_transformed
colnames(X_transformed.1) <- c("GDP","ServiceIndustry","Air","Population","MigrantWorker","Tourist")
autoplot(X_transformed.1, facets = TRUE) +
  xlab("Year") + ylab("Transformed")
autoplot(X_transformed.1 %>% diff() %>% diff() %>% diff(12),facets = TRUE) +
  xlab("Year") + ylab("Stationary") #stationary
autoplot(X_transformed.1 %>% diff() %>% diff() %>% diff(),facets = TRUE) +
  xlab("Year") + ylab("Stationary") #stationary
```


## d=2,D=1, NaNs produced in coefficient estimations of X predictors,aicc=-447.2
```{r}
auto.arima(log(Y) %>% diff() %>% diff() %>% diff(12),xreg=X_transformed %>% diff() %>% diff() %>% diff(12),stepwise = FALSE)
```
```{r}
X_transformed %>% diff() %>% diff() %>% diff(12)
```

### remove Tourist,aicc=-455.36
```{r}
auto.arima(log(Y) %>% diff() %>% diff() %>% diff(12),xreg=X_transformed[,c(1,2,3,4,5)] %>% diff() %>% diff() %>% diff(12),stepwise = FALSE)
```
### remove SI,aicc=-462.59
```{r}
auto.arima(log(Y) %>% diff() %>% diff() %>% diff(12),xreg=X_transformed[,c(1,3,4,5)] %>% diff() %>% diff() %>% diff(12),stepwise = FALSE)
```
### remove Population,aicc=-462.59
```{r}
auto.arima(log(Y) %>% diff() %>% diff() %>% diff(12),xreg=X_transformed[,c(1,3,5)] %>% diff() %>% diff() %>% diff(12),stepwise = FALSE)
```
### remove MigrantWorker,aicc=-496.64
```{r}
auto.arima(log(Y) %>% diff() %>% diff(12),xreg=X_transformed[,c(1,3)] %>% diff() %>% diff(12),stepwise = FALSE)
```
### residual:ARIMA(2,0,1)(0,0,2)[12],without constant, AICC=-496.64(BEST MODEL)
```{r}
Arima(log(Y) %>% diff() %>% diff(12),xreg=X_transformed[,c(1,3)] %>% diff() %>% diff(12), order = c(2,0,1), include.constant = FALSE, seasonal = c(0,0,2))
Arima(log(Y) %>% diff() %>% diff(12),xreg=X_transformed[,c(1,3)] %>% diff() %>% diff(12), order = c(2,0,1), seasonal = c(0,0,2), include.constant = FALSE) %>% checkresiduals() #whitenoise
fit.best <- Arima(log(Y) %>% diff() %>% diff(12),xreg=X_transformed[,c(1,3)] %>% diff() %>% diff(12), order = c(2,0,1), include.constant = FALSE, seasonal = c(0,0,2))
```

### mannually choose the order,ARIMA(0,0,3,0,0,2), aicc=-492.74
```{r}
ggtsdisplay(residuals(fit.best,type = "regression")) # seasonal MA(2)
adf.test(residuals(fit.best,type = "regression")) #stationary
```


```{r}
Arima(log(Y) %>% diff() %>% diff(12), xreg = X_transformed[,c(1,3)] %>% diff() %>% diff(12), seasonal = c(0,0,2)) #GDP is not significant
Arima(log(Y) %>% diff() %>% diff(12), xreg = X_transformed[,c(1,3)] %>% diff() %>% diff(12), seasonal = c(0,0,2)) %>% checkresiduals()
Arima(log(Y) %>% diff() %>% diff(12), xreg = X_transformed[,c(1,3)] %>% diff() %>% diff(12), seasonal = c(0,0,2)) %>% residuals() %>% ggtsdisplay()
Arima(log(Y) %>% diff() %>% diff(12), xreg = X_transformed[,c(1,3)] %>% diff() %>% diff(12), seasonal = c(0,0,2)) %>% residuals() %>% eacf() #ARMA(2,2) or MA(3)
#P=0,D=0,Q=2
Arima(log(Y) %>% diff() %>% diff(12), xreg = X_transformed[,c(1,3)] %>% diff() %>% diff(12), order = c(0,0,3),seasonal = c(0,0,2)) #ma2 is not significant
Arima(log(Y) %>% diff() %>% diff(12), xreg = X_transformed[,c(1,3)] %>% diff() %>% diff(12), order = c(0,0,3),seasonal = c(0,0,2), include.constant = FALSE, fixed = c(NA,0,NA,NA,NA,NA,NA)) #all coefficients are significant
fit.arimaX <- Arima(log(Y) %>% diff() %>% diff(12), xreg = X_transformed[,c(1,3)] %>% diff() %>% diff(12), order = c(0,0,3),seasonal = c(0,0,2), include.constant = FALSE, fixed = c(NA,0,NA,NA,NA,NA,NA)) %>% checkresiduals() #whitenoise,aicc=-492.74
fit.arimaX
```

## d=3,aicc=-434.29
```{r}
auto.arima(log(Y) %>% diff() %>% diff() %>% diff(),xreg = X_transformed %>% diff() %>% diff() %>% diff(),stepwise = FALSE)
```
### remove tourist,aicc=-424.56
```{r}
auto.arima(log(Y) %>% diff() %>% diff() %>% diff(),xreg = X_transformed[,c(1,2,3,4,5)] %>% diff() %>% diff() %>% diff(),stepwise = FALSE)
```
### remove MigrantWorker,aicc=-497.93
```{r}
auto.arima(log(Y) %>% diff()  %>% diff(12),xreg = X_transformed[,c(1,2,3,4)] %>% diff() %>% diff(12),stepwise = FALSE)
```
### remove SI,aicc=-498.42
```{r}
auto.arima(log(Y) %>% diff() %>% diff(12),xreg = X_transformed[,c(1,3,4)] %>% diff() %>% diff(12),stepwise = FALSE)
```
### remove Population,aicc=-496.64
```{r}
auto.arima(log(Y) %>% diff() %>% diff(12),xreg = X_transformed[,c(1,3)] %>% diff() %>% diff(12),stepwise = FALSE)
```

## forecast
```{r}
x <- ts(rbind(cbind(GDP_transformed,Air_transformed),cbind(fc_GDP$mean,fc_Air$mean)),start=c(2005,1),frequency = 12)%>%diff()%>%diff(12)
autoplot(x)
n <- length(x)/2
fc.best <- forecast(fit.best,xreg=x[(n-12):n,],h=13)
fc.best
autoplot(fc.best)
```

```{r}
Y1 <- diff(log(Y))[(length(Y)-12):(length(Y)-1)]
y1_12 <- Y1+fc.best$mean[1:12]
y1.13 <- y1_12[1]+fc.best$mean[13]
y1 <- append(y1_12,y1.13)
y <- rep(0,13)
for(i in seq(length(y1))){
  y[i] <- log(Y)[length(Y)]+sum(y1[1:i])
}
fc.y <- exp(y)
fc.y
autoplot(ts(append(Y,fc.y),start = c(2005,1),frequency = 12))
```


